Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-05-17 WRITEUP/ms.tex
minor edits

% temporal evolution in Cloud Dynamics
\AP{the following is cutting the discussion a bit too abruptly; additionally, it might seem contradicting with the fact that we find differences when analysing extreme stages}
We show the properties of all MCCs identified across all evolutionary stages in \Fig{alpha16-28}. We find no quantitative differences over the 700\,Myr traced in our simulation, except for the virial parameter, where the most relevant phases are shown in \Fig{alphaEvol} (see \Sec{singless}).

@@

We do not observe any significant temporal variations in the MCC dynamics over the course of 700\,Myr
traced in our simulation, except in the virial parameter, which is the lowest in the pre-starburst phase.
The virial parameter increases after a starburst as gas is self-regulated by feedback.

@@

We perform virial analysis, as motivated by \obs, where the virial parameter is used as a surrogate to comparing the potential to kinetic energies of
molecule gas structures. The high virial parameter found for some MCCs in \flower
indicates that they are not the collapsing structures and are found in regions of $Q_{\rm eff}>1$.
On the other hand, MCCs in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are unstable
and \SF is expected to take place within its star-forming {\it clumps} and {\it cores} on smaller scales,
where energy quickly dissipates. % with low virial parameters.
This is consistent with the notion that collapsing structures result from
gravitational instability occuring within globally stable structures, which are
supported by turbulence and rotation on large scale.
%%
%Our results suggest that the more massive and bigger MCCs compared to the Milky Way
%manifest from the higher gas mass fraction, surface density, and velocity dispersion, but \SF takes place on much smaller scales.
%Low-$Q$ sets the regions that fragments
%and within those regions where alphavir is low enough is where structures to further collapse to form stars.
This also implies \obs on spatially resolution better than $\simeq$40\,pc are needed to examine the truly star-forming structures (cores),
and thus, \SF in the first galaxies.

>>>>

% temporal evolution in Cloud Dynamics
We show the properties of all MCCs identified across all evolutionary stages in \Fig{alpha16-28}. 
One of the most pronounce differences in the dynamics of MCCs traced over the 700\,Myr shown in this work 
is seen in the virial parameter --- the most relevant phases are shown in \Fig{alphaEvol} (see \Sec{singless}).

@@

@@

We perform virial analysis, as motivated by \obs, where the virial parameter is used as a surrogate to comparing the potential to kinetic energies of
molecule gas structures. The high virial parameter found for some MCCs in \flower
indicates that they are not the collapsing structures and are found in regions of $Q_{\rm eff}>1$.
On the other hand, MCCs in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are unstable
and \SF is expected to take place within its star-forming {\it clumps} and {\it cores} on smaller scales,
where energy quickly dissipates. % with low virial parameters.
This is consistent with the notion that collapsing structures result from
gravitational instability occurring within globally stable structures, which are
supported by turbulence and rotation on large scale.
%%
%Our results suggest that the more massive and bigger MCCs compared to the Milky Way
%manifest from the higher gas mass fraction, surface density, and velocity dispersion, but \SF takes place on much smaller scales.
%Low-$Q$ sets the regions that fragments
%and within those regions where alphavir is low enough is where structures to further collapse to form stars.
This also implies \obs on spatially resolution better than $\simeq$40\,pc are needed to examine the truly star-forming structures (cores),
and thus, \SF in the first galaxies.

We examine temporal variations in the MCC dynamics over the course of 700\,Myr
traced in our simulation. One of the most prominent differences is the virial parameter, which is the lowest in the pre-starburst phase
but increases after a starburst as gas is self-regulated by feedback.
